Cover Times of Random Walks

### 2019-04-23 paper.tex
minor

We prove the following theorem and then use it to show that $\cov \sim \textrm{Pois}(e^{-x})$.
\begin{theorem}\label{thm:pois}
If $ne^{-r/n} \rightarrow \lambda \in [0, \infty)$, then the number of unvisited
vertices approaches a Poisson distribution with mean $\lambda$.
\end{theorem}

@@

We bound the expression from the top and the bottom and use the dominated convergence
theorem.
We will first show the upper bound.
Notice that $(1-x) \leq e^{-x}$ and recall our assumption that
$ne^{r/n} \rightarrow \lambda$.
Then
\begin{align}
{n \choose m} \left(1-\frac{m}{n}\right)^r &\leq \frac{n^m}{m!} e^{mr/n} \nonumber \\
&= \frac{(n e^{r/n})^m} {m!} \nonumber \\
&\rightarrow \frac{\lambda ^m} {m!} \nonumber
\end{align}

>>>>

We prove the following theorem and then use it to gain insight into the cover time
variable $\cov$.
\begin{theorem}\label{thm:pois}
If $ne^{-r/n} \rightarrow \lambda \in [0, \infty)$, then the number of unvisited
vertices approaches a Poisson distribution with mean $\lambda$.
\end{theorem}

@@

We bound the expression from the top and the bottom and use the dominated convergence
theorem to prove the previous limit.
We will first show the upper bound.
Notice that $(1-x) \leq e^{-x}$ and recall our assumption that
$ne^{r/n} \rightarrow \lambda$.
Then
\begin{align}
{n \choose m} \left(1-\frac{m}{n}\right)^r &\leq \frac{n^m}{m!} e^{mr/n} \nonumber \\
&= \frac{(n e^{r/n})^m} {m!} \nonumber \\
&\rightarrow \frac{\lambda ^m} {m!} \nonumber
\end{align}
